---
title: "Homework3"
author: "Jialiang Hua"
date: "10/17/2021"
output: github_document
---

```{r rsetup, message = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal())

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Let's load and describe the data!

```{r}
library(p8105.datasets)
data("instacart")
```

The "instacart" dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns.
Observations are items in orders by user. The dataset includes `r names(instacart)` variables.

* 1.1 How many aisles are there, and which aisles are the most items ordered from?
```{r}
aisle_df <- instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))
```

There are `r nrow(aisle_df)` aisles and the most items ordered aisle is fresh vegetables.

* 1.2 Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
```{r}
aisle_df %>% 
  filter(n > 10000) %>%
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n)
  ) %>% 
  ggplot(aes(x = aisle, y = n)) +
  theme(axis.text.x = element_text(angle = -90, vjust = 0.5, hjust = 0)) +
  geom_point()
```

* 1.3 Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%   group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(
    rank = rank(desc(n))
  ) %>% 
  filter(rank < 4) %>% 
  arrange(aisle, rank) %>% 
  knitr::kable() #print the table
```

* 1.4 Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).
```{r}
instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = "order_dow",
    values_from = "mean_hour"
  ) %>%
  knitr::kable() 
```


## Problem 2

Lets load the data!

```{r}
library(p8105.datasets)
data("brfss_smart2010")
```

Let's do some data cleaning!
```{r}
brfss_clean <- brfss_smart2010 %>%
  janitor::clean_names() %>% 
  filter(
    topic == "Overall Health", 
    response %in% c("Excellent", "Very good", "Good", "Fair", "Poor")
  ) %>%
  mutate(
    response = factor(response),
    response = fct_relevel(response, c("Poor", "Fair", "Good", "Very good", "Excellent"))
  )
```

* 2.1 In 2002, which states were observed at 7 or more locations? What about in 2010?
```{r}
states_observed_2002 = brfss_clean %>% 
  filter(year == 2002) %>%
  select(c(1, 2, 3)) %>% 
  distinct() %>% 
  count(locationabbr) %>% 
  filter(n >= 7)

states_observed_2010 = brfss_clean %>% 
  filter(year == 2010) %>%
  select(c(1, 2, 3)) %>% 
  distinct() %>% 
  count(locationabbr) %>% 
  filter(n >= 7)

states_observed_2002
states_observed_2010
```

According to the result, **6** states **(CT FL MA NC NJ PA)** were observed at 7 or more locations in 2002, while **14** states **(CA CO FL MA MD NC NE NJ NY OH PA SC TX WA)** were observed at 7 or more locations in 2010.

* 2.2 Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).

```{r excell}
excell_df =
  brfss_clean %>% 
  filter(response == "Excellent") %>% 
  select(year, locationabbr, data_value) %>% 
  group_by(year, locationabbr) %>% 
  summarize(mean_data = mean(data_value))
  
excell_df %>% 
  group_by(locationabbr) %>% 
  ggplot(aes(x = year, y = mean_data, color = locationabbr)) +
  geom_line(alpha = 0.5) +
  labs(
    title = "The mean data value of state vs year",
    y = "Mean data value", 
    x = "Year",
  ) +
  scale_colour_hue("State abb") +
  theme(legend.key.size = unit(0.02,'cm')) +
  theme(legend.key.width = unit(0.05,'cm'))
```

* 2.3 Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.
```{r}
brfss_clean %>%
  filter(locationabbr == "NY", year %in% c(2006, 2010)) %>%
  ggplot(aes(x = data_value, color = as.character(year))) +
  geom_density() +
  facet_grid(. ~ year) + 
  labs(title = "Distribution of data value of responses for 2006 and 2010 in NY State",
       x = "Data value of responses",
       y = "Density of data value")
```


## Problem 3

Let's load the data for problem 3!
```{r}
acc_df = read_csv("./data/accel_data.csv")
```

* 3.1 Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).
```{r}
acc_clean = 
  acc_df %>% 
  pivot_longer(
    activity.1:activity.1440,
    names_to = "minute",
    names_prefix = "activity.",
    values_to = "activity_counts"
  ) %>% 
  mutate(
      weekday = case_when(
      day %in% c("Monday","Tuesday","Wednesday","Thursday","Friday") ~ "weekday",
      day %in% c("Saturday","Sunday") ~ "weekend")
  ) %>% 
  mutate(
    day = as.factor(day),
    day = fct_relevel(day, 
      "Monday", "Tuesday", "Wednesday", "Thursday", "Friday" , "Saturday", "Sunday"),
    weekday = as.factor(weekday),
    minute = as.numeric(minute)
  )
```

This dataset is has `r nrow(acc_clean)` observations,  `r ncol(acc_clean)` columns. It contains `r names(acc_clean)` variables.

* 3.2 Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate across minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?
```{r}
acc_clean %>% 
  group_by(week, day) %>%
  summarize(total_activity = sum(activity_counts)) %>% 
  pivot_wider(
    names_from = day,
    values_from = total_activity
  ) %>% 
  knitr::kable()
```

I find from the table that the total activity on weekend in lower than the weekday.

* 3.3 Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.
```{r}
acc_clean %>% 
  ggplot(aes(x = minute, y = activity_counts, color = day, group = day_id)) +
  geom_line(alpha = 0.6) + 
  labs(
    title = "24-Hour Activity Count by Day",
    x = "Time",
    y = "Activity Count"
  ) + 
  scale_x_continuous(
    breaks = c(0, 360, 720, 1080, 1440), 
    labels = c("12a.m.", "6a.m.", "12p.m.", "6p.m.", "11:59p.m."),
    limits = c(0, 1440)
  ) +
  viridis::scale_color_viridis(
    name = "Location",
    discrete = "TRUE")
```

I can find that the activity level of the patient was low during 12a.m. to 6a.m.. There was a peak of activity around 12p.m. and 8p.m.

     
    


